Enter our title here

### 2017-09-13 manuscript.tex
changed code words/phrases to text-mode

1) should i add more about how it can be used in a flipped classroom?

2) how to get side by side pictures (for the teach editor code vs. preview)?

3) also, what is the best way to add pictures? They are not inserted in the pdf where i have the code

4) what are the bottom comments about the citations?

5) should i add that the courses are written in Hadley Wickham style?

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \cite{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citet{wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \cite{AmericanStatisticalAssociation2016}.

The goal for any introductory statistics course is to help students develope the ability to think statistically
\cite{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \cite{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \cite{Wang2017}.

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
\cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including Swirl (**need to cite this?
if so what should i cite**), LearnR and TryR. 
These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
systems (LMS) is not available for the classroom.

@@

Try R website --> \url{http://tryr.codeschool.com} i dont know how to cite this with mendeley
TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
introductory statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \cite{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

@@

DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses as well as specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses or assign a course that they've created for the particular class.

The collection of community courses avaiable at DataCamp inlcude a wide range of topics from 'Introduction to R' to
'Quantitative Risk Management in R' so novice through advanced programming students will benefit.
DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.

A feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
students had trouble with in a detailed report (datacamp/teach website). Student scores can be automatically updated to a
current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.

@@

\subsection{Pre-existing R courses}
DataCamp has a range of available free community courses that educators can utilize for supplimental R practice.

@@

The GitHub repository will contain three files: README.md, course.yml, and chapter1.Rmd.
Readme.md contains helpful information of how to get started, citing resourses to learn more about the process.
course.yml is a file that contains general information about the course you're creating: title, university, description,
difficulty level, ect.
chapter1.Rmd is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them chapter1.Rmd, chapter2.Rmd, chapter3.Rmd
ect.

@@

\begin{figure}[h]
  \includegraphics[scale = 0.2] {edit.jpg}
\end{figure}

>>>>

1) should i add more about how it can be used in a flipped classroom

2) should i add that the courses are written in Hadley Wickham style?
  - yes one sentence

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \cite{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citet{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \cite{AmericanStatisticalAssociation2016}.

The goal for any introductory statistics course is to help students develope the ability to think statistically
\cite{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \cite{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \cite{Wang2017}.

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
\cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including swirl (**need to cite this?
if so what should i cite**), LearnR and TryR. 
These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes swirl so popular is its versitality; educators can also create their own
lesson to fit the curriculum and assign it to students \cite{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
systems (LMS) is not available for the classroom.

@@

*Try R website  \url{http://tryr.codeschool.com} i dont know how to cite this with mendeley*

TryR (Code School 2014) is a web-based program and does not have swirls reproducible capability. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
introductory statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \cite{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

@@

DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses as well as specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
\textit{community} courses or assign a course that they've created for the particular class.

The collection of community courses avaiable at DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
\textit{Quantitative Risk Management in R} so novice through advanced programming students will benefit.
DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.

A feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
students had trouble with in a detailed report (cite datacamp/teach website?). Student scores can be automatically updated to a
current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.

@@

\subsection{Pre-existing R courses}
DataCamp has a range of available courses that educators can use as supplimental R practice. In order to utilize 
DataCamp's \textit{classroom} benefits, you will first need to create an academic group on the website \url{https://www.datacamp.com/groups/education}.
After your university information has been verified and the classroom account has been approved, you can add students by their university
email address on the \textit{Members} tab and link the account to your LMS.

@@

The GitHub repository will contain three files: \texttt{README.md}, \texttt{course.yml}, and \texttt{chapter1.Rmd}.
\texttt{Readme.md} contains helpful information of how to get started, citing resourses to learn more about the process.
\texttt{course.yml} is a file that contains general information about the course you're creating: title, university, description,
difficulty level, ect.
\texttt{chapter1.Rmd} is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them \texttt{chapter1.Rmd}, \texttt{chapter2.Rmd},
\texttt{chapter3.Rmd}, ect.

@@
